% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}

\usepackage{t1enc}  % allow accents
\usepackage[utf8]{inputenc} 

\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{\textit{André Leite Reis \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }}
\address{London, UK \\ 
         andre.reis@gmail.com \\ 
         Phone: +44 074 8210 1626 \\
         Linkedin: linkedin.com/in/andreleitereis \\
         Github: github.com/reis}

\begin{resume}
\section{Summary} BSc in Computer Science, having expertise in software development, 
                  data analysis and databases.
                        
                  20+ years of professional experience in IT working with different industries, 
                  methodologies and technologies.
                  
                  Experienced in business operations like Billing, CRM, sales pipeline, 
                  contact center managment, e-commerce, provisioning data center services, 
                  VOIP, telecomunications, higher education and research market.

\section{Skills Base}  
  \textbf{Programming Languages}: \LaTeX , PHP, Python, JavaScript and Java;\\
  \textbf{Data Science}: Strong SQL, PL/pgSQL, spreadsheets, plus some experiences with R;\\
  \textbf{Operating Systems}:  Linux (Arch, Debian, Ubuntu, CentOS, Fedora), Windows and OSX;\\
  \textbf{Networks}: Internet protocol suite, sockets, APIs, webservices; \\
  \textbf{Virtualization}: VirtualBox, VMWare, Xen, Cloudstack, Vagrant, PuPHPet;\\
                                  

\section{Experience}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Queen Mary University of London}    \>\>\textbf{Nov 2015 - Present}\\
    \textit{Software Developer}\\ \\       
    \textbf{Technologies}: Java, PHP, Python, Shell Script, Linux, Windows, Docker, RaspberryPi;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    I maintain and develop systems coding the front and back-end and new `interfaces` to integrate different systems. 

    Projects:
    \begin{itemize}
      \item Joint development with the University of Loughborough to develop a PHP web system (front and back-end)
      \item Python back-end interface between a commercial RGMS and the financial system using APIs
      \item Research Grants Managing System using PHP and Zend Framework
      \item Command line based Java tool to execute databases queries reading a XML data sources catalog
      \item Raspberry Pi with a RF Card Reader to collect attendance of NHS program students in offline locations (Python and Shell Script)
      \item Maintenance to a PHP Zend Framework intranet fixing bugs and creating new functions and reports
      \item Sync scripts to collect and update data between different systems reading and writing a wide range of formats (XML, JSON, web services, CSV, fixed length format files)
      \item Migrate websites from an external data-center to an internal Docker environment
      \item Optimize database views (PostgreSQL, Oracle and MS SQL Server)
    \end{itemize}

\vspace{5.0in}



\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Telium Networks}    \>\>\textbf{Jul 2006 - Aug 2015}\\
    \textit{Senior Software Developer} \\ \\        
    \textbf{Technologies}: Linux, PHP, Python, JS, PostgreSQL, MySQL, MongoDB, Git;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    My main role here is team leader on system analysis, writing code, testing and deploying process. I write a lot of code everyday but also attend to meetings with internal clients and lead daily stand up meetings with the all developers.

    Projects:
    \begin{itemize}
      \item Databases migrations changing encoding and PostgreSQL versions.
      \item Customer Control Panel (v1 CodeIgniter and v2 Laravel/Eloquent/Bootstrap).
      \item Sales Pipeline (v1 Code Igniter, PL/pgSQL, v2 Laravel/Eloquent/Bootstrap).
      \item Sales activities control (CodeIgniter).
      \item Event System for Contact Center (Symfony/Doctrine/ExtJS).
      \item Automation of services life-cycle (PHP).
      \item Updates on Billing System (Mojavi, Code Igniter).
      \item DNS database modeling and migration from a legacy system.
      \item Integration of Billing system with proprietary ERP Protheus.
      \item Dashboards, reports and alerts to the board.
      \item Several migration of DNS, web and email servers.
    \end{itemize}

In my spare time I like to study about programming languages such as Java, Ruby, Node.js, Python for data science and R.

\vspace{-0.1in}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{IFX}    \>\>\textbf{Dec 2000 - Jun 2006}\\
    \textit{Software Developer} \\ \\  
    \textbf{Technologies}: Linux, PHP, PostgreSQL, Oracle, MySQL and MS SQL;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
        Member of a team responsible to design and develop the intranet for the whole company over latin america. 
        It had to be a multi language, region with a complex permission system. It was also divided in modules and I was responsible for trouble tickets.
        Among other activities and projects, I attended a project to develop a billing system to charge recurrent services applying several business rules.
\vspace{-0.1in}

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Conex Internet Provider}    \>\>\textbf{Feb 1997 - Nov 2000}\\
    \textit{Junior Developer}\\ \\       
    \textbf{Technologies}: Visual Basic, ASP, MS SQL, Windows Server, IIS;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
      Dynamic websites development and web-server adminstration.  

\section{Education}	
      \textit{BSc in Computer Science} \\
            2001-2004 at Universidade Paulista, São Paulo, Brazil \\
            1999-2000 at Pontifícia Universidade Católica PUCRS, Porto Alegre, Brazil
      
      \textit{Computer Networks Technician} \\ 
            1997-1998 at Universidade Federal do Rio Grande do Sul, Porto Alegre, Brazil
      
      \textit{Data Processing Technician} \\
            1993-1996 at Escola Técnica Santo Inácio, Porto Alegre, Brazil
  
\section{Languages} 
  \begin{itemize}
    \vspace{2mm}
      \item \textbf{Portuguese}: Native
      \item \textbf{English}: Fluent
      \item \textbf{Spanish}: Basic
  \end{itemize}      

\section{Additional Training}
  \begin{itemize}
    \vspace{2mm}
      \item \textbf{ITIL}: ITIL Foundations (ITXL)
      \item \textbf{PMI}: Training course PMP-PMI (Euax)
      \item \textbf{Agile}: Agile Software Development (IME-USP)
      \item \textbf{Ruby on Rails}: RejectCode Ruby on Rails (IME-USP)
      \item \textbf{Java}: Java Course monitoring (UNIP)
      \item \textbf{MS SQL}: MS SQL Server Administrator (Microsoft Education Partner)
  \end{itemize}      
  
\section{Volunteering}
	\begin{itemize}
    \vspace{2mm}
      \item \textbf{East London}: Raising money for multi-ethnical youth clubs running The Big Half Race
		  \item \textbf{Ireland}: Sports lessons and recreation activities for children in a community center.\vspace{1mm}
		  \item \textbf{Israel and Palestine}: Gardening, sports lessons and recreation activities for children in summer camps.\vspace{1mm}
		  \item \textbf{Cananéia, Brazil}: Logistic support for medical assistance and sports lessons and recreation activities for children in risky areas.
	\end{itemize}

\end{resume} 
\end{document}
