\part{ANDRÉ LEITE REIS}
\label{andrÉleitereis}

Buckhurst Hill, Essex, UK
andre.reis@gmail.com
Phone: +44 074 8210 1626

\chapter{Summary}
\label{summary}

Bachelor in Computer Science, having expertise in software development, data analysis and databases.

With 19 years of professional experience in IT and experienced in business operations like billing, CRM, sales pipeline, contact center management, ecommerce, provisioning services and ITIL.

\chapter{Skills Base}
\label{skillsbase}

\emph{Operating System}: Linux (Arch, Debian, Ubuntu, CentOS, Fedora), Windows and OSX;

\emph{Networkings}: TCP\slash IP protocol suite;

\emph{Programming Languages}: PHP, Python, Shell Script, Java, JavaScript, plus some experience with Ruby;

\emph{Data Science}: Strong SQL, PL\slash pgSQL, Python and R;

\emph{Virtualization}: VirtualBox, VMWare, Xen, Cloudstack, Docker, Vagrant;

\part{Education}
\label{education}

\emph{BS in Computer Science} at Universidade Paulista UNIP, São Paulo, Brazil, December 2004.

** *\emph{BS in Computer Science} at PUC-RS, Porto Alegre, Brazil, December 2000 (incomplete transferred to UNIP).

\emph{Technical expertise in Networking} at Universidade Federal do Rio Grande do Sul (UFRGS), Porto Alegre, Brazil, December 1998.

\emph{Data Processing Technician} at Escola Técnica Santo Inácio, Porto Alegre, Brazil, December 1996.

\part{Experience}
\label{experience}

\textbf{Queen Mary University of London 							Nov 2015 - Current}

London, UK

\emph{System Analyst and Developer}

\textbf{Main Technologies:} Linux, PHP, Java, Shell Script, Python, PostgreSQL, Docker, RaspberryPi

I work developing apps using Java and Struts2, maintaining a PHP intranet, integrating the systems from different colleges using APIs, XML, JSON building scripts to sync data (Python, Java and Shell Script).

Projects:

\begin{itemize}
\item Research Grants Proposals Managing System using PHP and Zend Framework

\item Generic Java tool to execute databases queries from a XML catalog

\item Raspberry Pi with a RF Card Reader to collect attendance of NHS program students in offline (or almost) locations (Python and Linux admin issues)

\item Maintenance to a PHP Zend Framework intranet fixing bugs and creating new functions and reports

\item Sync scripts to collect and update data between different systems reading and writing a wide range of formats (XML, JSON, web services, CSV, fixed length format files)

\item Migrate websites from an external datacenter to an internal Docker environment

\item Optimize database views (PostgreSQL, Oracle and MS SQL Server)

\end{itemize}

**Telium Networks 									Jul 200\textbf{\textbf{6}} - **\textbf{Aug 2015}

Sao Paulo, Brasil
\emph{Senior Software Developer}
\textbf{Main Technologies}: Linux, PHP, Python, JS, PostgreSQL, MySQL, MongoDB, Git;

My main role there was team leader on system analysis, writing code, testing and deploying process. I wrote a lot of code everyday but also attend to meetings with internal clients and lead daily stand up meetings with the all developers.

Another role of mine was data analyst and consultant for the main board of the company generating several reports, spreadsheets and dashboards.

I was also the PostgreSQL administrator besides the sysadmins team being responsible for the server dimensioning, tablespaces structure, performance, tuning and migrations.

Projects:

\begin{itemize}
\item Databases migrations changing encoding and PostgreSQL versions.

\item Customer Control Panel (version 1 with CodeIgniter and version 2 with Laravel\slash Eloquent\slash Bootstrap).

\item Sales Pipeline (v1 Code Igniter, PL\slash pgSQL, v2 Laravel\slash Eloquent\slash Bootstrap).

\item Sales activities control (CodeIgniter).

\item Incidents Managing System for Contact Center (Symfony\slash Doctrine\slash ExtJS).

\item Automation of services lifecycle (PHP).

\item Updates on Billing System (PHP with Mojavi and Codeigniter).

\item DNS database modeling and migration from a legacy system.

\item Integration of Billing system with proprietary ERP Protheus.

\item Dashboards, reports and alerts to the board.

\item Several migration of DNS, web and email servers.

\end{itemize}

In my spare time I like to study about programming languages such as Java, Ruby, Node.js, Python for data science and R.

\textbf{IFX} 											\textbf{Dec 2000 - Jun 2006}
Sao Paulo, Brasil

\emph{Software Developer}
\textbf{Main Technologies}: Linux, PHP, PostgreSQL, Oracle, MySQL and MS SQL;

Member of a team responsible to design and develop the intranet for the whole company over latin america. It had to be a multi language, region with a complex permission system. It was also divided in modules and I was responsible for trouble tickets. Among other activities and projects, I attended a project to develop a billing system to charge recurrent services applying several business rules.

\textbf{Conex} 											\textbf{Feb 1997 - Nov 2000}

Porto Alegre, Brasil
\emph{Junior Developer}
\textbf{Main Technologies}: Visual Basic, ASP, MS SQL, Windows Server, IIS;

Dynamic websites development and web server administration.

\part{Languages}
\label{languages}

\begin{itemize}
\item \textbf{Portuguese}: Mother tongue

\item \textbf{English}: Fluent

\item \textbf{Spanish}: Basic

\end{itemize}

\part{Additional Training}
\label{additionaltraining}

\begin{itemize}
\item \textbf{ITIL}: ITIL Foundations (ITXL)

\item \textbf{PMI}: Training course PMP-PMI (Euax)

\item \textbf{Agile}: Agile Software Development (IME-USP)

\item \textbf{Ruby on Rails}: RejectCode Ruby on Rails Conference (IME-USP)

\item \textbf{Java}: Java teaching assistant (UNIP)

\item \textbf{MS SQL}: MS SQL Server Administrator (Microsoft Education Partner)

\end{itemize}

\part{Volunteering}
\label{volunteering}

\begin{itemize}
\item **Summer Camp in ****Ireland**: Sports lessons and recreation activities for children in a community center.

\item **Reconciliation experience in **\textbf{Israel and Palestine}: Gardening, sports lessons and recreation activities for children in summer camps.

\item **Logistic Assistant in **\textbf{Cananéia, Brazil}: Logistic support for medical assistance and sports lessons and recreation activities for children in risky areas.

\end{itemize}

\part{More Info}
\label{moreinfo}

\begin{itemize}
\item \textbf{Linkedin}: http:\slash \slash www.linkedin.com\slash in\slash andreleitereis

\item \textbf{Github}: https:\slash \slash github.com\slash reis\slash cv

\end{itemize}
