% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}

\usepackage{t1enc}              % Permite digitar os acentos de forma normal
\usepackage[utf8]{inputenc} 

\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{\textit{ANDRÉ LEITE REIS}}
\address{São Paulo, Brazil \\ andre.reis@gmail.com \\ Phone: +55 11 99328-9258 }
                           
                        
\begin{resume}                        
 
\section{Summary} Bachelor in Computer Science, having expertise in software development, data analysis and databases.
                        
                  With 19 years of professional experience in IT working basically with Linux, PHP (plain, Laravel, Symfony), PostgreSQL, pl/pgSQL, Mysql, Python, Shell Script, Nginx, Apache, MongoDB, Cloudstack, Vagrant, AWS, PuPHPet, EDI, ETL, Git, Subversion using agile methodologies. Experienced in business operations like Billing, CRM, sales pipeline, contact center, e-commerce, provisioning data center services, VOIP, telecomunications and ITIL.
 
\section{Education}	
  \begin{itemize}
    \item BS in Computer Science at Universidade Paulista, São Paulo, Brazil, December 2004.
    \item BS in Informatics at PUC-RS, Porto Alegre, Brazil, December 2000 (incomplete transfered to UNIP).
    \item Technical expertise in Networking at Universidade Federal do Rio Grande do Sul (UFRGS), Porto Alegre, Brazil, December 1998.
    \item Data Processing Technician at Escola Técnica Santo Inácio, Porto Alegre, Brazil, December 1996.
\end{itemize}

\section{Experience}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Telium}    \>\>\textbf{Jul 2006 - Present}\\
    \textit{Sr Software Developer}\\        
    \textbf{Main Technologies}: Linux, PHP, Python, JS, PostgreSQL, MySQL, MongoDB, Git;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
    My main role here is team leader on system analysis, writing code, testing and deploying process. I write a lot of code everyday but also attend to meetings with internal clients and lead daily stand up meetings with the all developers.

    Another role of mine is data scientist, analyst and consultant for the main board of the company generating several reports, spreadsheets and dashboards.

    I am also the PostgreSQL administrator besides the sysadmins team being responsible for the server dimensioning, tablespaces structure, performance, tunning and migrations.

    Projects:
    \begin{itemize}
      \item Databases migrations changing encoding and PostgreSQL versions.
      \item Customer Control Panel (v1 CodeIgniter and v2 Laravel/Eloquent/Bootstrap).
      \item Sales Pipeline (Code Igniter, PL / SQL, Laravel/Eloquent).
      \item Sales activities control (CodeIgniter).
      \item Event System for Contact Center (Symfony/Doctrine/ExtJS).
      \item Automation of services lifecyle (PHP).
      \item Updates on Billing System (Mojavi, Code Igniter).
      \item DNS database modeling and migration from a legacy system.
      \item Integration of Billing system with proprietary ERP Protheus.
      \item Dashboards, reports and alerts to the board.
      \item Several migration of database, web and e email servers.
    \end{itemize}

In my spare time I like to study about programming languages such as Java, Python for data analysis, JavaScript, R.

\vspace{-0.1in}

\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{IFX}    \>\>\textbf{Dec 2000 - Jun 2006}\\
    \textit{Software Developer}\\        
    \textbf{Main Technologies}: Linux, PHP, PostgreSQL, Oracle, MySQL and MS SQL;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
        Member of a team responsible to design and develop the intranet for the whole company over latin america. 
        It had to be a multi language, region with a complex permission system. It was also divided in modules and I was responsible for trouble tickets.
        Among other activities and projects, I attended a project to develop a billing system to charge recurrent services applying several business rules.
\vspace{-0.1in}

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.7in}\= \kill % set up two tab positions
    \textbf{Conex}    \>\>\textbf{Feb 1997 - Nov 2000}\\
    \textit{Jr Developer}\\        
    \textbf{Main Technologies}: Visual Basic, ASP, MS SQL, Windows Server, IIS;
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    \vspace{2mm}
      Dynamic websites development and webserver adminstration.  

\section{Skills Base}  \textit{Operating System}:  Linux (Arch, Debian, Ubuntu, CentOS, Fedora), Windows and OSX;

			\textit{Networkings}: TCP/IP protocol suite;
  
			\textit{Progamming Languages}: PHP, Python, JavaScript, plus some experience with Lua and Java;

      \textit{Data Science}: Strong SQL, PL/pgSQL, spreadsheets, plus some experiences with R;
  
			\textit{Virtualization}: VirtualBox, VMWare, Xen, Cloudstack, Vagrant, PuPHPet;

			\textit{Languages}: Fluent in Portuguese, Advanced in English and Basic in Spanish;


\section{Additional Training}
    \vspace{2mm}
      ITIL Foundations (ITXL)

      Training course PMP-PMI (Euax)

      Agile Software Development Laboratory (IME-USP)

      RejectCode Ruby on Rails (IME-USP)

      Java Course monitoring (UNIP)

      MS SQL Server Administrator (Microsoft Education Partner)
  
\section{Volunteer works}
		\begin{itemize}
		    \vspace{2mm}
		    \item \textbf{Ireland}: Sports lessons and recreation activities for children in a community center.\vspace{1mm}
		    \item \textbf{Israel and Palestine}: Gardening, sports lessons and recreation activities for children in summer camps.\vspace{1mm}
		    \item \textbf{Cananéia, Brazil}: Logistic support for medical assistance and sports lessons and recreation activities for children in risky areas.
		\end{itemize}
 
\section{More Info}
    \begin{itemize}
        \item \textbf{Linkedin}: http://www.linkedin.com/in/andreleitereis
        \item \textbf{Github}: https://github.com/reis
    \end{itemize}


\end{resume} 
\end{document}